%──────────────────────────────────────────────
%  Junjie Yu – Academic CV  (single-page, styled)
%  Compile:  pdflatex CV.tex  (run twice)
%──────────────────────────────────────────────
\documentclass[11pt,a4paper]{article}

% ─── Geometry ───
\usepackage[top=0.4in,bottom=0.4in,left=0.55in,right=0.55in]{geometry}

% ─── Fonts ───
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}

% ─── Colour & links ───
\usepackage[dvipsnames]{xcolor}
\definecolor{accent}{HTML}{1A5276}      % deep blue for headings
\definecolor{linkblue}{HTML}{2471A3}    % lighter blue for links
\definecolor{rulecolor}{HTML}{2E86C1}   % section rule color
\definecolor{muted}{HTML}{5D6D7E}       % muted text
\usepackage[colorlinks=true,urlcolor=linkblue,linkcolor=linkblue]{hyperref}

% ─── Icons ───
\usepackage{fontawesome5}

% ─── Lists ───
\usepackage{enumitem}
\setlist[itemize]{nosep,left=0pt .. 1.4em,label={\color{accent}\textbullet},topsep=1pt,itemsep=0.5pt}

% ─── Section formatting ───
\usepackage{titlesec}
\titleformat{\section}{%
  \color{accent}\normalsize\bfseries\uppercase%
}{}{0em}{}[\vspace{1pt}{\color{rulecolor}\hrule height 0.8pt}]
\titlespacing*{\section}{0pt}{7pt}{4pt}

% ─── Misc ───
\usepackage{tabularx}
\usepackage{graphicx}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ─── Helper: thin separator ───
\newcommand{\entrysep}{\vspace{3pt}}

% ─── Helper: experience entry ───
\newcommand{\entry}[4]{%
  \textbf{#1}\hfill{\color{muted}\textit{#2}}\\[-1pt]
  {\color{muted}#3}\hfill{\color{muted}\textit{#4}}\par\vspace{1pt}%
}

% ─── Helper: project entry ───
\newcommand{\projectentry}[3]{%
  {\small\href{#1}{\textbf{\color{accent}#2}} {\color{muted}|} #3}\par\vspace{1.5pt}%
}

% ─── Helper: award entry ───
\newcommand{\awardentry}[3]{%
  \textbf{#1}\hfill{\color{muted}#2}\\[-2pt]
  {\small\color{muted}#3}\par\vspace{2pt}%
}

\begin{document}

% ════════════════════════════════════════════
%  HEADER
% ════════════════════════════════════════════
\begin{center}
  {\fontsize{22}{26}\selectfont\bfseries\color{accent} Junjie Yu}\\[6pt]
  {\small\color{muted}%
    \faEnvelope\enspace\href{mailto:YuJunjie-yjj@sjtu.edu.cn}{YuJunjie-yjj@sjtu.edu.cn}%
    \enspace{\color{rulecolor}\textbar}\enspace%
    \faGlobe\enspace\href{https://junjieyu28.github.io}{junjieyu28.github.io}%
    \enspace{\color{rulecolor}\textbar}\enspace%
    \faGithub\enspace\href{https://github.com/JunjieYu28}{JunjieYu28}%
  }
\end{center}

\vspace{-2pt}

% ════════════════════════════════════════════
%  EDUCATION
% ════════════════════════════════════════════
\section{Education}

\entry{Shanghai Jiao Tong University}{Sep 2023 -- Present}
{BEng in Artificial Intelligence \enspace$\cdot$\enspace Zhiyuan Honors Program}{Shanghai, China}
{\small Average Score: 89.18\,/\,100 \enspace$\cdot$\enspace Rank: 34\,/\,98}

% ════════════════════════════════════════════
%  PUBLICATIONS
% ════════════════════════════════════════════
\section{Publications}

\begin{itemize}
  \item \href{https://arxiv.org/abs/2603.21986}{Speed by Simplicity: A Single-Stream Architecture for Fast Audio-Video Generative Foundation Model}.\\ \textit{arXiv preprint}, 2026.
\end{itemize}

% ════════════════════════════════════════════
%  RESEARCH EXPERIENCE
% ════════════════════════════════════════════
\section{Research Experience}

\entry{Research Internship}{Dec 2025 -- Present}
{SJTU \& SII -- \href{https://plms.ai/index.html}{GAIR Lab}\enspace$\cdot$\enspace Mentor: \href{https://plms.ai/}{Pengfei Liu}}{Shanghai, China}
\begin{itemize}
  \item First author \& Project leader of \textbf{AcademiClaw}, a benchmark for OpenClaw.
  \item Participant in \href{https://huggingface.co/GAIR/daVinci-MagiHuman}{\textbf{davinci-magihuman}}.
  \item Built downstream applications based on davinci-magihuman, including digital human meetings and digital human live streaming. {\small\color{muted}[Soon Public]}
  \item Participated in the development of \textbf{Wesay} (a speech recognition app). {\small\color{muted}[Private Repo]}
\end{itemize}

\entrysep

\entry{Research Internship}{Mar 2025 -- Dec 2025}
{SJTU -- Artificial Intelligence Institute, DeepVision Lab\enspace$\cdot$\enspace Mentor: \href{https://shenwei1231.github.io/}{Wei Shen}}{Shanghai, China}
\begin{itemize}
  \item Conducting research on \textbf{MultiModal Large Language Model}.
  \item Participated in training a GUI recognition model for future GUI Agent (collaborative project with Huawei). Responsible for data synthesis, annotation, and cleaning.
  \item Conducting research on \textbf{visual token pruning} for multimodal models.
\end{itemize}

\entrysep

\entry{Summer Research Internship}{Jul 2024 -- Sep 2024}
{SJTU -- Artificial Intelligence Institute, DeepVision Lab\enspace$\cdot$\enspace Mentor: \href{https://shenwei1231.github.io/}{Wei Shen}}{Shanghai, China}
\begin{itemize}
  \item Explored \textbf{Computer Vision} fundamentals; read research papers and reproduced basic CV algorithms.
\end{itemize}

% ════════════════════════════════════════════
%  PROJECTS
% ════════════════════════════════════════════
\section{Projects}

\projectentry{https://github.com/JunjieYu28/RAG-TA}{RAG-TA}
{A RAG Teaching Assistant System.\enspace\textit{\small Python}}

\projectentry{https://github.com/JunjieYu28/Paper-RAG}{Paper-RAG}
{An intent-aware paper recommendation and research assistant powered by RAG.\enspace\textit{\small Python}}

\projectentry{https://github.com/JunjieYu28/GUI-Project}{GUI-Project}
{Data preparation for training a GUI recognition model for future GUI Agent.\enspace\textit{\small Python}}

\projectentry{https://github.com/JunjieYu28/ViT-on-Image-Classification}{ViT-on-Image-Classification}
{ViT on image classification, esp.\ small-scale datasets (CIFAR-10).\enspace\textit{\small Jupyter Notebook}}

% ════════════════════════════════════════════
%  HONORS & AWARDS
% ════════════════════════════════════════════
\section{Honors \& Awards}

\awardentry{Zhiyuan Honors Scholarship}{2024, 2025}
{Award for top students majoring in science.}

\awardentry{Undergraduate Excellence Scholarship}{2024, 2025}
{Awarded to students with outstanding comprehensive evaluation rankings.}

% ════════════════════════════════════════════
%  RESEARCH INTERESTS
% ════════════════════════════════════════════
\section{Research Interests}

Agent,\enspace Multimodal,\enspace Large Language Model,\enspace AI for Games%
\hfill{\color{accent}\textbf{Current Focus:}} Agent \& Multimodal

% ════════════════════════════════════════════
%  SKILLS
% ════════════════════════════════════════════
\section{Skills}

\begin{tabularx}{\textwidth}{@{}>{\bfseries\color{accent}}l@{\enspace}X@{}}
  Programming & Python, C++ \\
  Agent       & Claude Code, Codex, Cursor, OpenClaw \\
  Tools       & Git, Linux, \LaTeX, Docker, PyTorch \\
  Languages   & Chinese (native), English (fluent) \\
\end{tabularx}

\end{document}
